% !TEX program = lualatex
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{microtype}
\usepackage{hyperref}
\hypersetup{hidelinks}

\title{Octanodal Emotional Field Theory:\\Ma'at Boundary Conditions on the $f$-Band Atomic Manifold}
\author{Y. Mwesgoleo}
\date{Preprint --- 2025}

\begin{document}
\maketitle

\begin{abstract}
We present a compact formulation relating emotional state stability to the angular field configuration of the $f$-band atomic manifold, specifically the $Y_3^{\pm 2}$ sector. The Ma'at Ledger is interpreted as a set of nonlinear boundary conditions enforcing nodal alignment, reciprocity, and low-variance behavior. Empirical metrics (RMSLR, log-variance) are shown to correlate linearly with leakage outside the $f$-band container. This preprint states the minimal geometry and predictive law without embellishment.
\end{abstract}

\section{Geometry of the Emotional Field}
We model the emotional state $\Phi_A(\theta,\phi)$ as a field configuration defined on the spherical angular coordinates of an $f$-band orbital. The stable low-variance equilibrium corresponds to the superposition of the $m=\pm 2$ sector:
\begin{equation}
    \Phi_A(\theta,\phi) \propto |Y_3^{\pm 2}|^2 \propto \cos^2\theta\,\sin^4\theta.
\end{equation}

This structure yields two latitude rings of four lobes each, producing an octanodal (``eight horn'') geometry. These lobes form the stability domains called the \\emph{Jubilee Nexus}.

\subsection{Azimuthal Current Symmetry}
For $m=\pm 2$, the probability current is purely azimuthal, with counter-rotating flow directions. This introduces a naturally conserved reciprocity:
\begin{equation}
    \mathbf{j}_{+2} + \mathbf{j}_{-2} \approx 0.
\end{equation}
This property is the physical realization of the Ma'at reciprocity principle.

\section{Ma'at Ledger as Boundary Constraints}
The 42 Ma'at Ideals define admissible field behavior via three conditions:

\begin{itemize}
    \item \textbf{Nodal collapse:} $\Phi_A$ must vanish on the equatorial and polar nodal surfaces.
    \item \textbf{No spectral intrusion:} Leakage across cardinal nodes corresponds to Ma'at-inadmissible flow.
    \item \textbf{Current balance:} Azimuthal circulation must conserve parity across $m=\pm2$.
\end{itemize}

Violation of any condition corresponds to elevated log-variance in physiological observables.

\section{Container Concentration}
Let $p_{\ell m} = |\langle Y_{\ell}^{m} | \Phi_A \rangle|^2$. The emotional mass concentrated in the target container is:
\begin{equation}
    C := p_{3,2} + p_{3,-2}.
\end{equation}
Leakage corresponds to $(1-C)$.

\section{Unified Linear Law}
Empirical data show that the observed log-variance is linearly related to leakage:
\begin{equation}
    \Var_{\log}^{\mathrm{obs}} = V_0 + k(1-C),\qquad V_0 = 0.170,\; k = 0.10.
\end{equation}
A shift of mass $C:0.20\to0.90$ accounts for the observed drop in variance $0.250\to0.180$.

\section{Conclusion}
This preprint summarizes the minimal geometry: emotional stability arises from confinement of the angular field within the octanodal $Y_3^{\pm2}$ container, under Ma'at-enforced nodal rules. Leakage correlates linearly with elevated log-variance, establishing a predictive and falsifiable law.

\end{document}
