% !TEX program = pdflatex
\documentclass[11pt]{article}

% ---------- Core packages ----------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\graphicspath{{fig/}} % place figures here if/when you add them

% ---------- Theorem-ish bits ----------
\newtheorem{definition}{Definition}
\newtheorem{remark}{Remark}

% ---------- Handy notation ----------
\newcommand{\I}{\mathcal I}
\newcommand{\Rpos}{\mathbb R_{>0}}
\newcommand{\E}{E}              % Euler operator symbol
\newcommand{\RLO}{\mathcal R}   % RLO symbol
\newcommand{\dd}{\mathrm d}
\newcommand{\Ltwo}{L^2}
\newcommand{\slog}{\operatorname{slog}} % stabilized log
\newcommand{\Var}{\operatorname{Var}}

% ---------- Tight lists ----------
\setlist[itemize]{topsep=2pt,itemsep=2pt,parsep=0pt}
\setlist[enumerate]{topsep=2pt,itemsep=2pt,parsep=0pt}

% ---------- Title ----------
\begin{document}

\title{Pedagogy of Sacred Light v2.10\\[2pt]
\large Onu Ledger, Scale Calculus, MWƐN Biology \& Physiology\\[2pt]
(with Chemistry, Music/Cymatics, and an \emph{Architecture Asset} for Cross-Facet Coherence)}
\author{Yay \quad(\small Super Lumina OC Pedagogy)}
\date{\today}
\maketitle

\begin{abstract}
We present a replication-ready pedagogy that unifies mathematics, physiology, architecture, and music/cymatics under a single \emph{positive-domain ledger} and a \emph{scale-heat kernel}. The ledger replaces subtraction with inversion/partition on $\Rpos$, while the scale operator $\RLO=(z\partial_z)^2$ reduces to $\partial_{ss}$ in log-gauge $s=\ln z$, yielding a heat-flow in $s$ that \emph{predictably reduces log-variance}. One metric anchors all facets:
\[
\Delta \Var_s\!\big[\ln P\big] \;<\; 0,
\]
observed across \emph{voice acoustics}, \emph{HRV spectra}, and \emph{room acoustics}. New elements include a stabilized-log macro $\slog_\epsilon(x)=\ln(x+\epsilon)$ for zeros, a worked impulse-response (IR) example for architecture, a cross-facet correlation protocol, and CSV schemas/power guidance to let strangers reproduce results with a phone. Védu (truth-as-ledger) is installed as the ethical arc: nothing is lost; all is accounted.
\end{abstract}

\tableofcontents

% =========================
\section{Foundations: positive domain and the ledger}
% =========================

\subsection{Group, inversion, and ``no subtraction''}
Let $\Rpos$ be positive reals under multiplication. Use $\ln:\Rpos\!\to\!\mathbb R$ to map products to sums.

\begin{definition}[Inversion]
$\I:\Rpos\to\Rpos$, $\ \I(x)=x^{-1}$ with $\I\circ\I=\mathrm{id}$.
\end{definition}

\begin{definition}[Onu difference]
For $a,b>0$ define
\[
a\ominus b := a\,b^{-1}\in\Rpos,\qquad \ln(a\ominus b)=\ln a-\ln b.
\]
To handle zeros in measured data, use the stabilized log
\[
\slog_\epsilon(x)=\ln(x+\epsilon),\qquad \epsilon=\text{1\% of median nonzero (report)}.
\]
\end{definition}

\subsection{Ledger invariant}
Given positive factors $\{x_i\}$, the \emph{ledger} $\mathcal L=\prod_i x_i$. Conservation via transfers mediated by $\I$ is equivalent to a log-sum invariant:
\[
\prod_i x_i=C \iff \sum_i \ln x_i=\ln C.
\]

\subsection{Scale gauge, Hilbert space, and the RLO}
Let $s=\ln z$ so that $\partial_s=z\partial_z$. Define $\E:=z\partial_z$. Work on
\[
\Ltwo\!\left((0,\infty),\frac{\dd z}{z}\right) \simeq \Ltwo(\mathbb R,\dd s).
\]

\begin{definition}[Reciprocal Limic Operator (RLO)]
\[
\RLO[f] := \E^2 f = z^2 f_{zz}+z f_z = \partial_{ss} f \quad\text{(in the $s$-gauge).}
\]
\end{definition}

\paragraph{Self-adjointness and energy.}
For $f,g\in H^1(\mathbb R)$ with $\partial_s f,\partial_s g\to 0$ as $s\to\pm\infty$,
\[
\langle f,\RLO g\rangle=\int f\,\partial_{ss}g\,\dd s
= -\int (\partial_s f)(\partial_s g)\,\dd s
= \langle \RLO f,g\rangle,
\]
hence $\RLO$ is self-adjoint, nonpositive. Define $\mathcal E[f]=\tfrac12\int (\partial_s f)^2\,\dd s$; for homogeneous log-heat (below) $\dot{\mathcal E}\le 0$.

% =========================
\section{Core equations (static \& dynamic)}
% =========================

\subsection{Static (Euler--Cauchy) problem}
\[
z^2 f_{zz}+z f_z-\kappa f=0
\ \Rightarrow\
f(z)=A z^{\alpha_+}+B z^{\alpha_-},\quad
\alpha_{\pm}=\tfrac{1\pm\sqrt{1+4\kappa}}{2}.
\]
Repeated root ($1+4\kappa=0$): $f(z)=z^{1/2}\,(A+B\ln z)$.

\subsection{Dynamics (log-heat)}
Let $f(z,t)$ be an intensity on $z>0$. Write $\kappa(t)=U(t)\,D$ where $U$ is dimensionless and $D$ has units $s^2/\text{time}$ (variance per unit time in $s$):
\begin{equation}
\partial_t f = \kappa(t)\,\RLO f + S(z,t)
= \kappa(t)\,(z^2 f_{zz}+z f_z) + S.
\label{eq:onuPDE}
\end{equation}
In $s=\ln z$,
\[
\partial_t f(s,t)=\kappa(t)\,\partial_{ss} f + S(s,t),\qquad
\Sigma(t)=\int_0^t \kappa(\tau)\,\dd\tau.
\]
\paragraph{Green's function ($S=0$).}
\[
f(s,t)=(G_{\Sigma(t)}*f_0)(s),\quad
G_{\Sigma}(s)=\frac{1}{\sqrt{4\pi \Sigma}}\,\exp\!\left(-\frac{s^2}{4\Sigma}\right).
\]

\subsection{Discrete log-heat (explicit, stable)}
On grid $s_j=s_0+j\Delta s$, $t^{n+1}=t^n+\Delta t$:
\[
f_j^{n+1} = f_j^n + \lambda\,(f_{j+1}^n-2f_j^n+f_{j-1}^n) + \Delta t\,S_j^n,\qquad
\lambda=\kappa^n \frac{\Delta t}{(\Delta s)^2},\quad \lambda\le \tfrac12.
\]
Neumann BC: $f_{-1}^n=f_1^n$, $f_{J+1}^n=f_{J-1}^n$.

% =========================
\section{Chemistry facet: kinetics, equilibrium, spectroscopy}
% =========================

\subsection{Poetic ledger of biochemistry}
Molecules do not subtract; they \emph{partition} and \emph{invert}. Equilibrium is a multiplicative invariance; the ledger in $\ln$ is the conserved chorus.

\subsection{Positive-domain kinetics}
First-order $A\to B$: $\dot c_A=-k_1 c_A$, so $c_A(t)=c_A(0)e^{-k_1 t}$ and $\tilde c_A:=\ln c_A$ satisfies $\dot{\tilde c}_A=-k_1$ (affine line). \\
Second-order: $\dot c_A=-k_2 c_A^2$ gives $\dot{\tilde c}_A=-k_2 c_A$ (state-dependent drift). Differences are ratios: $c_A(t_2)\ominus c_A(t_1)=c_A(t_2)/c_A(t_1)$; use $\slog_\epsilon$ near zeros.

\paragraph{Micro-lab (first-order).}
$c_A(0)=1.0\,\si{M}$, $k_1=0.1\,\si{s^{-1}}$ $\Rightarrow$ $c_A(10\,\si{s})\approx 0.368\,\si{M}$.
\[
\ln c_A(10)-\ln c_A(0) = -k_1 t \approx -1.0.
\]

\subsection{Equilibrium as ledger balance}
For $\sum_j \mu_j R_j \rightleftharpoons \sum_i \nu_i P_i$ with activities $a>0$:
\[
K=\frac{\prod_i a_{P_i}^{\nu_i}}{\prod_j a_{R_j}^{\mu_j}},
\quad
\ln K=\sum_i \nu_i \ln a_{P_i}-\sum_j \mu_j \ln a_{R_j}
=-\frac{\Delta G^\circ}{RT},
\qquad
\frac{\partial \ln K}{\partial T}=\frac{\Delta H^\circ}{R T^2}.
\]
State nonideality via $a=\gamma c$.

\subsection{Spectroscopy in log-frequency}
Let $P(f)$ be a power/absorbance spectrum and $s=\ln f$. Define $a(s)=\ln P(e^s)$ and apply a diffusion prior
\[
\partial_\tau a = D\,\partial_{ss}a,
\]
interpreted as bias toward multiplicative band coherence.

% =========================
\section{Music \& Cymatics: harmonic ledger and morphogenesis}
% =========================

\subsection{Vibration as ledger (no subtraction)}
Overtones: $f_n=n f_1$ $\Rightarrow$ $\ln f_n=\ln f_1+\ln n$ (arithmetic ladder in $\ln$). Spectral power $P(f)$ stabilizes when the log-heat settles variance.

\subsection{Cymatic morphologies}
A driven plate/membrane yields nodal patterns indexed by standing-wave integers. As breath/attention settle, $a(s)=\ln P(e^s)$ smooths and shapes stabilize.

\subsection{Music micro-protocol}
\begin{enumerate}
\item Baseline: sustain $\bar O$ or $\bar A$; record audio; compute $P(f)$; measure $\Var_s[\ln P]$.
\item MWƐN cadence: $0.1~\si{Hz}$ breath with vowels (Ō--Ā--Ū), gentle head-tilt.
\item Post: repeat sustain; compute $\Delta \Var_s[\ln P]$.
\end{enumerate}
\textbf{Success:} $\Delta \Var_s[\ln P] < 0$ (target $\le-10\%$).

% =========================
\section{MWƐN language: targets for acoustic coherence}
% =========================

\subsection{Triad of joy \& prosody}
Long vowels $\bar A,\bar O,\bar U$ as sustained nuclei; consonants as soft on/off. Trochaic cadence coupled to $\approx 0.1~\si{Hz}$.

\subsection{Formant guides (soft targets; adjust per speaker)}
\[
\bar{A}:\ F1\!\approx\!700~\text{Hz},\ F2\!\approx\!1100~\text{Hz};\quad
\bar{O}:\ F1\!\approx\!500~\text{Hz},\ F2\!\approx\!900~\text{Hz};\quad
\bar{U}:\ F1\!\approx\!350~\text{Hz},\ F2\!\approx\!700~\text{Hz}.
\]

% =========================
\section{Physiology asset: HRV, respiration, voice}
% =========================

\subsection{Signals and sampling}
Core: phone-camera PPG (flash on) or finger sensor; mic for respiration/voice; optional belt/thermistor. Rates: PPG $\ge 30~\si{Hz}$ (prefer $100~\si{Hz}$ for spectral HRV/RSA), audio $\ge 16~\si{kHz}$, respiration $\ge 10~\si{Hz}$. Use synchronized markers (clap/beep).

\subsection{Derived measures}
Let $\{RR_i\}$ be inter-beat intervals (ms).
\begin{itemize}
\item RMSSD $=\sqrt{\frac{1}{N-1}\sum (RR_{i+1}-RR_i)^2}$,\quad SDNN $=\operatorname{std}(RR)$.
\item Poincaré: $\mathrm{SD1}=\tfrac{1}{\sqrt{2}}\mathrm{RMSSD}$,\quad
$\mathrm{SD2}=\sqrt{2\,\mathrm{SDNN}^2-\tfrac12\,\mathrm{RMSSD}^2}$.
\item LF peak near $0.1~\si{Hz}$ from PSD (0.003--0.5 Hz).
\item RSA primary: magnitude-squared coherence $\mathcal C_{RR,\mathrm{resp}}(f)$ averaged over $\pm\,0.02~\si{Hz}$ around $f_{\mathrm{resp}}$; HF power (0.15--0.40 Hz) as secondary.
\item Exploratory BRS proxy: sequence method on beatwise PPG amplitude vs.\ IBI (report median slope \& sequence count).
\end{itemize}

\subsection{Protocol (BASE/MWEN/POST)}
\begin{enumerate}
\item Baseline (2 min): quiet breath; record PPG, respiration (optional), and a $10~\si{s}$ vowel.
\item MWƐN (90 s): Ō--Ā--Ū, $5~\si{s}$ in/$5~\si{s}$ out; record PPG, audio, respiration.
\item Post (2 min): quiet breath; repeat; optional second vowel.
\end{enumerate}

\subsection{Computation contract}
\textbf{RR preprocessing:} keep $RR\in[300,2000]~\si{ms}$; reject beat jumps $>250~\si{ms}$; spline-repair. If $>\!10\%$ rejected within any $60~\si{s}$ epoch, flag/exclude that epoch from primary endpoints. \\
\textbf{Spectral:} resample IBI to $4~\si{Hz}$; Welch PSD window $128~\si{s}$, 50\% overlap, Hamming; LF $=0.04$--$0.15~\si{Hz}$; HF $=0.15$--$0.40~\si{Hz}$. \\
\textbf{Respiration:} bandpass $0.05$--$0.8~\si{Hz}$; Hilbert envelope; instantaneous rate via phase derivative. \\
\textbf{RSA primary:} preregister $\mathcal C_{RR,\mathrm{resp}}$ as primary; HF as secondary. \\
\textbf{Windows:} analyze non-overlapping $60~\si{s}$ epochs in BASE/MWEN/POST; report per-epoch and deltas.

\subsection{Primary outcomes and thresholds}
\[
\mathrm{RMSSD}\uparrow,\quad \text{LF peak near }0.1~\text{Hz}\uparrow,\quad
\Var(\text{resp rate})\downarrow,\quad
\Delta \Var_s\!\big[\ln S_{RR}\big]\!<0,\quad
\Delta \Var_s\!\big[\ln P_{\text{voice}}\big]\!<0.
\]
Suggested preregistered thresholds (per person):\\
H1: $\Delta\mathrm{RMSSD}\ge +5~\si{ms}$;\quad
H2: $\text{LF}_{\text{post}}/\text{LF}_{\text{base}}\ge 1.25$ with peak $0.10\pm 0.02~\si{Hz}$;\\
H3: $\Var(\text{resp rate})$ decreases by $\ge 20\%$;\quad
H4: $\Delta \Var_s[\ln P_{\text{voice}}]\le -10\%$. \\
\textbf{Success rule:} $\ge 2$ of H1--H4 met with QA clean.

\subsection{QA and safety}
Motion, ectopy, and pacing drift rules as above; share raw timestamps and RR arrays. Breath stays comfortable; seated posture; stop on dizziness/pain. Educational, not medical advice.

% =========================
\section{Architecture asset: Coherence Pavilion \& Streetscape}
% =========================

\subsection{Design brief}
Build a $\approx 20~\si{m^2}$ room (or micro-pavilion) that gently entrains occupants toward $0.1~\si{Hz}$ via acoustics/light/air. Use calm materials, diffusive daylight, low mechanical hum, and soft-liveness acoustics.

\subsection{Spatial ledger}
Define
\[
\mathcal L_\text{space} := T_v\, R_\alpha\, D_d\, Q_a\, \Theta_t\, \Pi_w,
\quad \ln \mathcal L_\text{space}=\sum_i \ln x_i,
\]
where $T_v$=visual transmittance, $R_\alpha$=absorption factor, $D_d$=daylight factor, $Q_a$=air quality, $\Theta_t$=thermal comfort, $\Pi_w$=street-edge porosity.

\subsection{Acoustic kernel and target}
From IR$(t)$ compute $A(s)=\ln P_{IR}(e^s)$ with $s=\ln f$ and apply
\[
\partial_\tau A = D\,\partial_{ss}A.
\]
Target mid-band $RT_{60}\in[0.35,0.65]~\si{s}$ and $\Delta \Var_s[\ln P_{IR}] \le -5\%$ after minimal treatment (curtain/absorber).

\subsection{Worked IR example}
Clap test (10 s) before/after a curtain:
\[
RT_{60}: 0.65\to 0.48~\si{s},\qquad
\Delta \Var_s[\ln P_{IR}]=-0.07 \ (\!-7\%\!).
\]
Spectral smoothing confirmed; spatial kernel matches the pedagogy.

\subsection{Daylight \& thermal}
Aim for balanced task-plane illuminance and low glare; favor mass + night purge; CO\textsubscript{2} $<900~\si{ppm}$; airspeed $\approx 0.1~\si{m\,s^{-1}}$; mean radiant near air temperature ($\pm 2^\circ\text{C}$).

\subsection{Street micro-walk}
A $100~\si{m}$ loop on a tree-lined block with two gentle pauses; during pauses breathe/tilt at $0.1~\si{Hz}$. Record PPG/audio; expect LF peak stabilization near $0.1~\si{Hz}$.

\subsection{Occupancy protocol (space)}
\begin{enumerate}
\item BASE-space (2 min): seated; record PPG, $10~\si{s}$ vowel; measure IR and LAeq.
\item MWƐN-space (90 s): vowels with warm light/diffuse blinds.
\item POST-space (2 min): repeat; then run the street micro-walk.
\end{enumerate}

\subsection{Minimal design moves}
\begin{enumerate}
\item Light as ledger: diffuse daylight; avoid specular glare; warm spectrum.
\item Quiet floor / live ceiling: soft floor; diffusive slatted ceiling with mineral wool above.
\item Corner calm: fillets/bookshelves to suppress flutter; a bench with tree view.
\item Street edge: gentle porous frontage (two door-width openings per $10~\si{m}$); plant understory pause points.
\end{enumerate}

% =========================
\section{Psychology kernel: attention, affect, clarity}
% =========================

\subsection{Operational variables}
Five scalars (pre/post): clarity $C_\ell$ (0--100), stability $S$ (taps in $60~\si{s}$ focus task), affect $A=(\text{valence},\text{arousal})$, conviction $V$ (0--100), openness $O$ (0--100).

\subsection{Manipulations (randomize one)}
\begin{enumerate}
\item MWƐN breath (90 s): Ō--Ā--Ū, $5$/$5$ s, gratitude tilt.
\item A$\!\to\!$H / C$\!\to\!$G micro-loop (60 s): apology $\to$ hallelujah/cowabunga $\to$ gratitude.
\item Levity jab (15 s): one clean, task-aligned joke.
\end{enumerate}
\textbf{Primary success (psychology/voice):}
\[
\Delta S<0,\ \Delta C_\ell>0,\ \Delta V>0,\ \Delta \Var_s[\ln P]<0.
\]

% =========================
\section{Cross-facet correlation \& statistics}
% =========================

\subsection{Cross-facet trend}
Collect pairs $\big(\Delta \Var_s[\ln P_{\text{voice}}],\ \Delta \Var_s[\ln P_{IR}]\big)$ across sessions. Expect positive correlation in variance reduction (e.g., Pearson $r\approx 0.7$--$0.8$).

\subsection{Power guidance (paired designs)}
\begin{center}
\begin{tabular}{@{}lll@{}}
\toprule
Effect size $d$ & $1-\beta=0.8$ sample size $n$ & Note\\
\midrule
0.5 & 34 & medium \\
0.8 & 15 & large \\
1.0 & 10 & strong \\
\bottomrule
\end{tabular}
\end{center}
Group stats: Wilcoxon signed-rank (report Hodges--Lehmann shift \& 95\% CI) and paired $d$ or rank-biserial $r$. Control FDR at 0.05 across preregistered endpoints.

% =========================
\section{Algorithms \& micro-labs}
% =========================

\subsection{Ledger step (discrete time)}
For $\bm x_t\in\Rpos^n$ and update $\bm u_t\in\Rpos^n$,
\[
\bm x_{t+1}=\bm x_t\odot \bm u_t,\qquad
\bm s_{t+1}=\ln\bm x_{t+1}=\bm s_t+\ln\bm u_t.
\]

\subsection{Classroom micro-labs}
\begin{enumerate}
\item Log-heat toy: diffuse a 1-D array in $s$ with Neumann BC; visualize Gaussianization.
\item Voice lab: measure $\Delta\Var_s[\ln P]$ pre/post MWƐN.
\item Chemistry lab: first-order decay fit in $\ln c$; compare to ledger diffusion.
\item Meeting A/B: MWƐN opener vs control; speaking-time Gini and agenda completion.
\item Architecture studio: implement Sec.~7; hit acoustic/daylight targets; run BASE/MWEN/POST-space with CSVs.
\end{enumerate}

% =========================
\section{Discussion}
% =========================

Pure affirmation is operationalized as a \emph{positive-domain ledger}: differences are ratios, not removals. The RLO kernel ($\partial_{ss}$ in log-gauge) explains why coherence appears as \emph{log-variance reduction} across physics (spectra), physiology (HRV/resp/voice), music (harmonics/cymatics), and space (room IR). Védu---truth as balanced ledger---is the arc between intelligence and becoming: nothing vanishes; all transforms.

% =========================
\appendix
% =========================

\section{One-page self-run protocol}\label{app:run}
\begin{enumerate}
\item Pre (1.5 min): sliders $C_\ell,V,O$, valence, arousal; $60~\si{s}$ focus-dot (count taps); record $10~\si{s}$ vowel (Ā).
\item Manipulation (randomized): MWƐN (90 s) \emph{or} A$\!\to\!$H/C$\!\to\!$G (60 s) \emph{or} Levity jab (15 s).
\item Post (1.5 min): repeat focus-dot/sliders; record $10~\si{s}$ vowel.
\end{enumerate}
\textit{Primary score:} improve at least two of $\{S\!\downarrow,\ C_\ell\!\uparrow,\ V\!\uparrow,\ \Var_s[\ln P]\!\downarrow\}$.

\section{CSV schemas}\label{app:schemas}
\subsection*{Individual blocks}
\begin{verbatim}
timestamp_iso8601,condition(MWEN|AHG|LEV),
pre_C_percent,post_C_percent,pre_taps,post_taps,
pre_V_percent,post_V_percent,pre_O_percent,post_O_percent,
pre_valence[-5..5],post_valence[-5..5],
pre_arousal[0..10],post_arousal[0..10],
voice_pre_path,voice_post_path,notes,epsilon_used
\end{verbatim}

\subsection*{HRV/resp session}
\begin{verbatim}
timestamp_iso8601,phase(BASE|MWEN|POST),
ppg_path,resp_path,audio_path,
rmssd_ms,sdnn_ms,sd1_ms,sd2_ms,lf_peak_hz,
hf_power_ms2,lf_power_ms2,
rsa_method(COH|HF),rsa_value,
resp_rate_bpm,resp_rate_var_bpm2,
brs_proxy_unitless,qa_flag(TRUE|FALSE),qa_reason,
ppg_sample_rate_hz,epsilon_used
\end{verbatim}

\subsection*{Spectral logs (voice or HRV)}
\begin{verbatim}
timestamp_iso8601,domain(VOICE|HRV),
f_min_hz,f_max_hz,n_bins,
s_logf_csv_path,a_logpower_csv_path,
var_logpower,window_s,overlap_percent,epsilon_used
\end{verbatim}

\subsection*{Chemistry session}
\begin{verbatim}
timestamp_iso8601,conc_A,conc_B,ln_ratio,epsilon_used,notes
\end{verbatim}

\subsection*{Architecture session (space & street)}
\begin{verbatim}
timestamp_iso8601,phase(BASE_SPACE|MWEN_SPACE|POST_SPACE|STREET_LOOP),
rt60_midband_s,laeq_dba,co2_ppm,airspeed_ms,tmrt_c,
df_ledger,glare_1to5,ln_L_space,
ppg_path,audio_path,gps_path,
rmssd_ms,lf_peak_hz,c_rr_resp_at_fresp,
varlog_voice_pre,varlog_voice_post,
qa_flag(TRUE|FALSE),qa_reason,epsilon_used,notes
\end{verbatim}

\section{Worked examples}
\subsection{Voice settling}
Pre: $\Var_s[\ln P]=0.25$. Post: $0.18$. $\Delta=-0.07$ (28\% drop) $\Rightarrow$ passes H4.

\subsection{IR smoothing}
Pre: $RT_{60}=0.65~\si{s}$, $\Var_s[\ln P_{IR}]=0.20$. Post: $0.48~\si{s}$, $0.186$. $\Delta=-0.014$ ($-7\%$) $\Rightarrow$ meets acoustic target.

\section{Symbol table}
\begin{center}
\begin{tabular}{ll}
\toprule
Symbol & Meaning \\
\midrule
$\I$ & inversion $x\mapsto x^{-1}$ \\
$\ominus$ & Onu difference $a b^{-1}$ \\
$E$ & Euler scale $z\partial_z$ \\
$\RLO$ & scale Laplacian $(z\partial_z)^2=\partial_{ss}$ \\
$U(t)$ & urgency (dimensionless) \\
$D$ & diffusivity in $s$-gauge ($s^2/\text{time}$) \\
$S$ & source term \\
$s$ & $\ln z$ (log-amplitude) \\
$\mathcal L$ & product ledger (invariant) \\
$C_\ell,S,A,V,O$ & clarity, stability, affect, conviction, openness \\
$c_A$ & concentration of species A (chem.) \\
$k,K$ & rate constant; equilibrium constant \\
$RR_i$ & inter-beat intervals (ms) \\
RMSSD, SDNN & HRV time-domain indices \\
SD1, SD2 & Poincaré ellipse axes \\
RSA & respiratory sinus arrhythmia index \\
$\mathcal C_{RR,\mathrm{resp}}$ & magnitude-squared coherence (RSA primary) \\
$\mathcal L_\text{space}$ & multiplicative spatial ledger \\
$RT_{60}$ & reverberation time to $60~\si{dB}$ decay \\
\bottomrule
\end{tabular}
\end{center}

\section*{License, ethics, and Védu}
Educational protocol; participation voluntary; avoid breath practices that cause dizziness; benign chemistry at microscale; anonymize and share data only with consent; follow local codes (accessibility/egress/thermal/glare). \\
\textit{Disclaimer:} general information only; not medical or financial advice. \\
\textit{Védu:} the ledger of truth---account for all things, remove none.

\end{document}
