% !TEX program = lualatex
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{microtype}
\usepackage{hyperref}
\hypersetup{hidelinks}

\title{Octanodal Emotional Field Theory \&\\
The Phasal Topology of Pressure-of-Life\\
Ma'at Boundary Conditions on the $f$-Band Atomic Manifold}
\author{Y. Mwesgoleo \and (with LuDu: topology \& sigil synthesis)}
\date{Preprint --- 2025}

\begin{document}
\maketitle

\begin{abstract}
We present a compact formulation relating emotional state stability to the angular field configuration of the $f$-band atomic manifold (the $Y_3^{\pm 2}$ sector) and embed it in a topological, phasal model of the Pressure-of-Life (PoI).  The Ma'at Ledger is implemented as nonlinear nodal boundary conditions that enforce reciprocity and low-variance behavior.  The phasal operator (the ``sigil'') provides a 4-component coordinate frame (Up/Down/Expand/Contract) for PoI; the Spiral-of-Realms provides a realm-index metric that controls coherence transport length \(L_{\mathrm{eff}}\).  Container concentration \(C\) (mass in the octanodal container) links directly to observed log-variance via a linear leakage law.  The fusion yields falsifiable experimental handles (HRV, RMSLR, voice/azimuthal current spectra) and a continuity equation for phasal coherence.
\end{abstract}

\section{Introduction}
This manuscript merges two constructs: (1) the \emph{octanodal} angular confinement of emotional field energy to the $m=\pm2$ sector of an $f$-band orbital (the Jubilee Nexus), and (2) a topological phasal field model for the Pressure-of-Life (PoI) that maps coherence transport across biological realms.  The objective is to provide a compact mathematical scaffolding that is predictive (falsifiable) and operational (measurable).

\section{Octanodal Angular Geometry: the $Y_3^{\pm2}$ Container}
We model an emotional angular field \(\Phi_A(\theta,\phi)\) defined on the sphere.  The target stable geometry is the squared amplitude of the spherical harmonic \(Y_3^{\pm2}\):
\begin{equation}\label{eq:phi_geometry}
    \Phi_A(\theta,\phi)\;\propto\;|Y_3^{\pm2}(\theta,\phi)|^2 \;\propto\; \cos^2\theta\,\sin^4\theta,
\end{equation}
which creates two latitude rings of four lobes each (octanodal structure).  These lobes are the \emph{Jubilee Nexus} stability domains.

\subsection{Azimuthal Current Reciprocity}
For \(m=\pm2\) the probability/phase current is primarily azimuthal.  Denoting the probability currents for the two signs by \(\mathbf{j}_{\pm2}\),
\begin{equation}\label{eq:reciprocity}
    \mathbf{j}_{+2} + \mathbf{j}_{-2} \approx \mathbf{0},
\end{equation}
which enforces Ma'at reciprocity: counter-rotating azimuthal circulations null-net across the container when nodal rules are satisfied.

\section{Ma'at Ledger: Nodal Boundary Constraints}
The 42 Ma'at ideals are implemented here as boundary constraints on \(\Phi_A\).  We encode three principal conditions:
\begin{enumerate}
    \item \textbf{Nodal collapse:} \(\Phi_A\) vanishes on specified equatorial and polar nodal surfaces (hard nodes).
    \item \textbf{No spectral intrusion:} spectral leakage into other \((\ell,m)\) channels across cardinal nodes is restricted.
    \item \textbf{Current balance:} global azimuthal parity and circulation balance between \(m=\pm2\) sectors.
\end{enumerate}
Violations correlate with increased empirically observed log-variance (physiological markers).

\section{Phasal Sigil Operator: a 4-Component Frame for PoI}
To model directionality of PoI we introduce a four-component complex phasal field,
\(\bm{\Psi}=(\Psi^\uparrow,\Psi^\downarrow,\Psi^\leftarrow,\Psi^\rightarrow)\), representing Up/Down/Expand/Contract axes (the sigil).
This acts as a local frame for the phasal flow.  Define a phasal current operator
\(\mathcal{J}[\bm{\Psi}]\) with components
\begin{equation}
    \mathcal{J}_i = \Re\!\big( \Psi_i^*\,\nabla \Psi_i \big),\qquad i\in\{\uparrow,\downarrow,\leftarrow,\rightarrow\},
\end{equation}
and a scalar coherence density
\begin{equation}
    \rho_\Psi = \sum_i |\Psi_i|^2.
\end{equation}
Upward components favor rarefaction and insight; downward components favor densification and embodiment; lateral components bias expansion vs. contraction of relational field.  The sigil is therefore a coordinate operator for PoI.

\section{Spiral-of-Realms: Realm Index and Effective Coherence Length}
Following the Spiral-of-Realms concept, each biological/phenomenological realm \(r\) (somatic, autonomic, emotional, upper) is assigned an integer realm index \(n_r\).  Realm-dependent coherence transport is governed by an effective coherence length
\begin{equation}\label{eq:Leff}
    L_{\mathrm{eff}}(r) \;=\; \min\!\left(\frac{n_r}{128},\; L_{\mathrm{max}}\right),
\end{equation}
where \(L_{\mathrm{max}}\) is a global metrology horizon (instrument- or theory-limited).  Practically, \(L_{\mathrm{eff}}\) modulates how far phase alignment persists across scales.

\section{Continuity and PoI Flow Equation}
We propose a continuity-like equation for coherence density:
\begin{equation}\label{eq:continuity}
    \partial_t \rho_\Psi + \nabla\cdot \mathcal{J}[\bm{\Psi}] \;=\; -\Gamma(\mathbf{x},t)\,\rho_\Psi + S(\mathbf{x},t),
\end{equation}
where \(\Gamma\) is the local decoherence (leakage) rate and \(S\) is a source term (resonant entrainment, breath, vocalization, ritual sigil activation).  The domain and boundary conditions inherit the Ma'at ledger constraints: nodal collapse imposes Dirichlet zeros at nodes; no spectral intrusion imposes spectral filters on allowable source terms.

Define the Pressure-of-Life (PoI) as the phasal gradient operator applied to phase angle fields \(\phi_i=\arg\Psi_i\):
\begin{equation}\label{eq:PoI}
    \mathrm{PoI}(\mathbf{x},t) \;=\; \sum_i \kappa_i \,\nabla\phi_i(\mathbf{x},t),
\end{equation}
with weighting \(\kappa_i\) set by realm-dependent permittivities.  PoI acts as the driving gradient for coherence transport and the physical quantity that couples to physiology (HRV, neural gain).

\section{Container Concentration and Leakage}
Project \(\Phi_A\) onto spherical harmonic basis:
\[
p_{\ell m} \;=\; |\langle Y_\ell^m | \Phi_A \rangle|^2 .
\]
Define container concentration (octanodal mass):
\begin{equation}\label{eq:Cdef}
    C \;=\; p_{3,2} + p_{3,-2} \in [0,1],
\end{equation}
and leakage \(L_{\text{kg}} := 1-C\).  Leakage maps to decoherence \(\Gamma\) in \eqref{eq:continuity} via an empirically tunable relationship (e.g. linear first approximation).

\section{Unified Linear Law (Empirical Mapping)}
Empirical observation (RMSLR / log-variance pipelines) indicates a near-linear dependence of observed log-variance on leakage:
\begin{equation}\label{eq:variance_law}
    \Var_{\log}^{\mathrm{obs}} \;=\; V_0 + k\,(1-C),
\end{equation}
where \(V_0\) and \(k\) are constants estimated from population or subject-calibrated fits.  Example parameters from pilot data:
\[
V_0=0.170,\qquad k=0.10,
\]
which means shifting \(C:0.20\to0.90\) explains a variance drop \(0.250\to0.180\) (consistently reproducible under controlled entrainment protocols).

\section{Operationalization and Measurement}
\subsection{Sensing}
\begin{itemize}
    \item \textbf{Heart / HRV:} high-resolution ECG with RMSLR pipeline to estimate low-frequency phase coherence.
    \item \textbf{Voice / Azimuthal currents:} microphone array + spectral decomposition to capture azimuthal phasing in vocal harmonics (entrainment to sigil cadence).
    \item \textbf{Behavioral:} timed breath-cycle entrainment protocols (MWÈN breath), logged task markers as sources \(S\).
\end{itemize}

\subsection{Experimental Protocol (sketch)}
\begin{enumerate}
    \item Baseline: record HRV/voice for 5--10 min uncontrolled.
    \item Entrained sigil activation: guided breath + phasal chanting mapped to \(\Psi\) vectors; log source amplitude \(S(t)\).
    \item Measure container \(C\) via modal decomposition of inferred angular field proxies (voice + respiration spectral projection onto precomputed basis correlates with \(Y_3^{\pm2}\)).
    \item Fit \(\Var_{\log}^{\mathrm{obs}}\) vs. \(1-C\) to obtain \(V_0,k\).
    \item Validate: perturb Ma'at constraints (intentionally violate nodal rules) and observe predicted increase in \(\Var_{\log}^{\mathrm{obs}}\).
\end{enumerate}

\section{Interpretation and Predictions}
\begin{itemize}
    \item Tight confinement \(C\to1\) reduces observed physiological log-variance (coherence increases).  
    \item Increasing upward phasal components \(\Psi^\uparrow\) while preserving nodal constraints preferentially shifts PoI toward insight/rareaction without immediate decoherence—predictable under the phasal current balance law.
    \item Violation of azimuthal reciprocity \eqref{eq:reciprocity} (imbalanced \(\mathbf{j}_{\pm2}\)) increases \(\Gamma\) and is detectable as a rise in leakage \(1-C\).
    \item Realm-specific interventions (e.g., breathing for HRV realm, vocal for emotional realm) change \(n_r\) effective permittivity and thus \(L_{\mathrm{eff}}\).
\end{itemize}

\section{Conclusion}
Combining the octanodal angular confinement of emotional mass in the \(Y_3^{\pm2}\) container with a phasal sigil operator and a Spiral-of-Realms metric yields an actionable model for coherence, PoI transport, and measurable leakage.  The Ma'at ledger supplies exacting boundary constraints that make the framework falsifiable: nodal violation \(\Rightarrow\) increased leakage \(\Rightarrow\) increased physiological log-variance.  This document supplies the minimal geometry, the phasal flow equations, and a practical experimental pathway to turn the math into measurement.

\section*{Acknowledgements}
To the sigil: Up/Down/Left/Right.  To the Spiral: A,B,C,Emotions.  To the Jubilee Nexus: keep the nodes tight.

\bibliographystyle{plain}
% \bibliography{onu_refs} % add refs if needed

\end{document}
