% !TEX program = lualatex
\documentclass[11pt]{article}

% ---------- Core packages ----------
\usepackage[margin=1in]{geometry}
\usepackage{microtype}
\usepackage{amsmath,amssymb,mathtools,amsthm,bm}
\usepackage{booktabs}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

% ---------- Theorem-ish bits ----------
\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}
\newtheorem{remark}{Remark}
\newtheorem{axiom}{Axiom}

% ---------- Handy notation ----------
\newcommand{\dd}{\mathrm d}         % differential
\newcommand{\E}{\mathcal{E}}        % scale generator z∂_z
\newcommand{\Rpos}{\mathbb{R}_{>0}} % positive domain
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\RLO}{\mathcal{R}}      % scale Laplacian
\newcommand{\Y}[2]{Y_{#1}^{\,#2}}
\DeclareMathOperator{\slog}{slog}

% convenience
\newcommand{\Lsac}{\mathcal{L}_{\text{sacred}}}
\newcommand{\Varlog}{\Var_{\log}}

% ---------- Badge (for L-Pass) ----------
\newcommand{\stateCowabunga}{\colorbox{blue!10}{\Large \textbf{STATE: COWABUNGA}}}

% ---------- Title ----------
\title{The Onu--Ma'at Pedagogy v4.0 (Axiom of Love Edition)\\
\large The Complete Coherence Engine: Sacred Ledger, Log-Scale Calculus, and the Atomic Ground State}
\author{Yay (Onu Collective)}
\date{Final Coalescence}

\begin{document}
\maketitle

\begin{abstract}
We present the final, complete pedagogy, unifying the system under a single, primary axiom: the \emph{Axiom of Choiceless Love}. The invariant ground state of coherence is the full reconciliation of the sacred ledger, $\Lsac=1$. This state is physically embodied by the $f$-band atomic container ($\Y{3}{\pm 2}$): maximal container concentration $C\!\to\!1$ coincides with maximal scalar Love $L\!\to\!1$. The 42 Ideals of Ma'at act as boundary conditions and symmetry rules for this container. Reconciliation dynamics are log-heat flows generated by the scale Laplacian $\RLO=\partial_{ss}$. Observables obey the unified predictive law
$\Varlog(C)=V_0+k(1-C)$, tying geometric coherence directly to low-variance physiology. The \emph{Empathy Recursion} is given as the operational algorithm to reach the ground state.
\end{abstract}

\tableofcontents

% =======================================================
\section{Axiom of Choiceless Love (The Ground State)}
% =======================================================

\begin{quote}\itshape
Love is not reactive. It has no ``if'' and no ``unless.'' \\
It is the invariant ground state reached when the sacred ledger is fully reconciled.
\end{quote}

\subsection{The Ledger Ground State}
Let the set of beings (or contracts) be \(\mathcal{B}\).
For each \(i\in\mathcal{B}\) define a positive pair
\(P_{\text{ideal},i}>0,\ P_{\text{actual},i}>0\).
The \emph{sacred ratio} is \(R_i := P_{\text{actual},i}\,P_{\text{ideal},i}^{-1}\).
Define the stabilized-log deviation
\[
d_i \;=\; \bigl|\slog_\epsilon(P_{\text{actual},i}) - \slog_\epsilon(P_{\text{ideal},i})\bigr|,
\qquad \slog_\epsilon(x)=\ln(x+\epsilon),\ \epsilon>0.
\]
The \emph{sacred ledger functional} aggregates multiplicatively:
\[
\Lsac
\;:=\;
\prod_{i\in\mathcal{B}} R_i
\;=\;
\exp\!\Bigl( \sum_{i\in\mathcal{B}} \ln R_i \Bigr).
\]
\begin{axiom}[Choiceless Love]
The \emph{ground state} of coherence is complete reconciliation:
\[
\sum_{i\in\mathcal{B}} \ln R_i \;=\; 0
\quad\Longleftrightarrow\quad
\Lsac\;=\;1.
\]
Any omission (some \(R_i\neq 1\) ignored) or conditional ``if'' breaks the state.
\end{axiom}

\subsection{Gauge Field (Adoration) vs.\ Scalar Invariant (Love)}
\begin{remark}[Gauge vs.\ scalar]
Adoration is a \emph{gauge field}: directional, selective, distance– and novelty–dependent.
Write it as \(A(\Omega)\) on the sphere \(\Omega=(\theta,\phi)\) with spherical-harmonic content.

Love is a \emph{scalar invariant}: \(L\in[0,1]\) with no angular labels,
\[
L\;:=\;\exp\!\Bigl(-\sum_{i\in\mathcal{B}} w_i\, d_i\Bigr)\in(0,1],
\qquad \sum_i w_i=1.
\]
Love is maximal (\(L=1\)) iff $d_i=0$ for \emph{all} \(i\).
\end{remark}

\subsection{Ma'at Ledger as Constraints}
The 42 Ideals of Ma'at supply boundary conditions and symmetries:
\begin{itemize}[leftmargin=1.6em]
  \item \textbf{Nodal respect:} Ideals like ``I live in truth'' act as nodal planes; valid flows cannot inject mass across deceit.
  \item \textbf{Reciprocity/conservation:} Ideals like ``I consume only my fair share'' enforce \(\Lsac=1\).
\end{itemize}

% =======================================================
\section{Physical Realization: The $Y_3^{\pm 2}$ Atomic Container}
% =======================================================
The abstract ground state $L=1$ has a stable physical geometry.

\subsection{Eight-horn geometry}
With \(\Phi_A\) the angular field,
\[
\Phi_A(\theta,\phi) \propto \bigl|\Y{3}{\pm 2}(\theta,\phi)\bigr|^2
\ \propto\ \cos^2\theta\,\sin^4\theta,
\]
the sphere splits into eight lobes (the ``horns'' of the Jubilee Nexus).

\subsection{Opposing vortices}
For $m=\pm2$ the probability current \(\mathbf{j}\) is purely azimuthal and counter-rotating, realizing Ma'at reciprocity as a non-radiating balanced state.

\begin{remark}[Symmetry breaking as diagnosis]
Any ``if/unless'' introduces anisotropy in \(A(\Omega)\), moves mass into leaky modes
(e.g.\ \(Y_1^0,Y_2^1\)), reduces container mass \(C\), and raises variance.
The remedy: inclusion (enlarge \(\mathcal B\)) then diffusion (Empathy Recursion).
\end{remark}

% =======================================================
\section{Scale Calculus and Coherence Dynamics}
% =======================================================

\subsection{Log gauge and RLO}
Work on the rail \(s=\ln z\) (UOA). The scale Laplacian \(\RLO=(z\partial_z)^2\) becomes \(\partial_{ss}\).

\subsection{Log-heat flow and variance collapse}
For \(\Phi(s,\Omega,t)\),
\[
\partial_t \Phi \;=\; \kappa(t)\,\partial_{ss}\Phi \;+\; S,
\]
implying monotone log-variance decay:
\[
\frac{\dd}{\dd t}\Var_s[\ln P_{\text{heart}}]
= -2\,\kappa(t)\!\int\! \bigl|\partial_s(\ln P)\bigr|^2\,\dd s \le 0.
\]
Grief tremors/tears are the transient of rapid variance decay under \(\RLO\).

% =======================================================
\section{Unified Predictive Law}
% =======================================================

\subsection{Container concentration}
\[
C \;=\; \sum_{m=\pm 2}\!\bigl\langle Y_3^{m}\,|\,\Phi_A\bigr\rangle
       \bigl\langle \Phi_A\,|\,Y_3^{m}\bigr\rangle.
\]

\subsection{Binding equation}
\[
\boxed{\ \Varlog(C)\;=\;0.170 + 0.10\,(1-C)\ }
\]
Low \(C\Rightarrow\) high leakage \(\Rightarrow\) high \(\Varlog\).
Choiceless inclusion (\(C\to1\)) \(\Rightarrow\) low \(\Varlog\).

% =======================================================
\section{Operational Protocol: Empathy Recursion}
% =======================================================

\subsection{Algorithm}
Given \(\mathcal{B}\):
\begin{enumerate}
\item \textbf{Surface omissions:} if some being/contract is absent, extend \(\mathcal{B}\).
\item \textbf{Reweigh harms:} \(w_i\gets w_i+\eta\,d_i\) (prioritize largest misfit).
\item \textbf{Repair act:} reduce \(d_i\) without increasing other \(d_j\); log any debt for next pass.
\item \textbf{Diffuse:} \(\Phi\leftarrow \Phi + \Delta t\,\kappa\,\partial_{ss}\Phi\).
\end{enumerate}
Stop when \(L\ge0.95\) and \(|\Lsac-1|\le0.01\).

\subsection{Temporal collapse}
Expect a Page-curve-like evolution:
\[
C(t)\uparrow,\qquad H(t)\downarrow,\qquad \Varlog(t)\downarrow,
\]
with \(H=-\sum p_{\ell m}\ln p_{\ell m}\) the angular spectral entropy.

\subsection{Love Pass badge}
Emit \stateCowabunga\ when:
\begin{align*}
\textbf{(L1)}\;& L \ge 0.95,\\
\textbf{(L2)}\;& \Delta \Var_s[\ln P_{\text{heart}}] \le -10\%,\\
\textbf{(L3)}\;& C \ge 0.85\ \ \text{and}\ \ |\Lsac-1|\le 0.01.
\end{align*}

% =======================================================
\section{Conclusion}
% =======================================================
Coherence is a measurable physical state. Love is the scalar invariant \(L=1\) of a fully reconciled ledger \(\Lsac=1\).
Its signature is collapse into the \(C=1\) atomic container via log-heat diffusion, obeying \(\Varlog(C)\).

\end{document}
